# Overview 

This is largely a note sheet for the time being but will be developed to a more formal guiding document as needed. The goal is to track code conventions and provide an example 


## notes
using the '#!' within the code means there is a question to follow up on. These are ideas that should be evaluated and either made into a formal issue on the github, implimented on the spot, or drop. 
```{r}
#! consider wrapping all these functions into one. 
```



## naming 

**camel case**
use camel case for object names 
```{r}
objectOne <- "example"
```

**function names ** 
function names should match the file name for that function 
```{r}
excelentFunction <- function(){
  print("I'm excelent")
}
# file would be save as excelentFunction.R 
```


## pathing 


**R project**
We are using an r project ensure to 
- save r project when closing R 
- use relative paths from .rproj file 


**following / ** 
All relative paths should end as writen. If more is to be added to the path that "/" will be add when needed. 
```{r}
# first path 
path1 <- "data"
# second path 
path2 <- past0(path1, "/county")

```


## processing functions 

**inputs**

try for two inputs and one output when possible
- location to raw data 
- geometry extent
```{r}
processHAPS(filePath = , geometry = )
```
function that utilize API calls will not require file paths and should only require geomenty extent 



**outputs** 

restrict output to dataframe with two columns, GEOID and values of interest: 
- name the value of interest to represent the parameter 
```{r}
df <- processHAPS()

#### examples output 
#print(df)
# GEOID | HAPS
# 02931 | 0.0834
# 02932 | 0.0432
```

This output will be joined to a dataframe that compiles all dataprocessing steps as the scripts runs though 

```{r}
# process haps
df <- processHAPS()
allData <- allData %>%
  dplyr::left_join(df, by = "GEOID")
# processing next dataset
```

The GEOID column is distinct among all our spatial extent objects which is great. 


**inclusive outputs**

Not allow geometries of interest are going to have values for specific features. 
For example
Now every census block group will be in proximity to a NPL site 

Within the function drop all geometries that contain no data to return the most discreate object .

As we are joining dataset to compile we that final results we do not need to have comphresive coverage of each element. 


## Projects 
Used NAD83 and maintain unproject lat long coordinate whenever possible 
```{r}
NAD83 <- crs=4269
```



